Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description

### 2020-10-28 paper/main.tex
rewrite intro

\section{Introduction}
\todo[inline]{I wonder whether we should make a general point: The construction
  of contrasts of interests feels "messy". But this is a consequence of the
  inability to filter the stimulus material. That "messy" part is usually not obvious from a manuscript.
  Here we have a fixed, complex stimulus, and we have to operationalize our questions with whatever we
have at hand. This is not necessarily exact, and looking at the robustness is a feature, not a problem}
\todo[inline]{Limit for main text (intro and discussion) = ca. 3k words;
intro is about 1k words (with to dos)}

\todo[inline]{retrosplenial cortex is not mentioned in intro anymore but it
shows up in group results (mixed in individual subjects) and therefore should
be discussed}

% brain mapping via fMRI
Cognitive neuroscientists use brain imaging methods like blood oxygenation
level-dependent functional magnetic resonance imaging (BOLD fMRI) to map
perceptual and cognitive brain processes (e.g. viewing of faces
\citep{kanwisher1997ffa} or theory of mind \citep{spunt2014validating}) to
functional brain areas or networks.\todo{kinda aggressive introductory
sentence}.
% What is the PPA?
A classic example of a functionally defined, higher-level visual area is the
``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
epstein1999parahippocampal}.
% anatomical location != functional location
The PPA is located in the posterior parahippocampal gyrus including adjacent
regions of the fusiform gyrus and anterior lingual gyrus
\citep{epstein2008parahippocampal}.
% neural correlate of scene perception
Increased hemodynamic activity in the PPA correlates with the perception of
static pictures of landscapes, buildings or landmarks \citep{aguirre1998area,
epstein2014neural, epstein1998ppa} compared to e.g. pictures of tools of faces.
% spatial layout hypothesis
[[According to the spatial layout hypothesis, the PPA is involved in processing
the surface geometry of a visual stimulus and possibly in identifying scenes
based on their spatial layout \citep{epstein2010reliable}.]]\todo{better delete}
% literature review overview 1: imagination & haptic exploration
At a group average level, results generalize \todo{MIH: more specific? what generalizes? just some location?} to mental imagination of landscapes
\citep{ocraven2000mental} and haptic exploration of scenes constructed from LEGO
blocks \citep{wolbers2011modality}.
% literature review overview 2: spoken sentences
One study that used spoken, place-related sentences showed significantly
decreased activation in the left and no modulation in the right-hemispheric PPA
\citep{aziz2008modulation}.

% literature review in detail
% O'Craven: Mental imagery
In the study conducted by \cite{ocraven2000mental} participants viewed
alternating blocks of pictures showing famous faces and familiar places during
an initial experimental paradigm. In a subsequent paradigm, participants were
instructed to ``form a vivid mental image'' of the previously viewed pictures.
The PPA showed increased activation during imagination of places compared to
faces but the imagination tasks showed a smaller activation level compared to
the perceptual task.

% Wolbers: haptic exploration
In the block design study conducted by \cite{wolbers2011modality} the PPA of
sighted participants showed increased activation during a delayed
match-to-sample task of haptically explored scenes constructed from LEGO
bricks compared to haptically explored abstract geometric objects.
% connectivity analysis by Wolbers
\todo[inline]{Wolbers performed connectivity analysis between PPA and occipital
cortex, and compares connectivity during visual and haptic paradigm: ``The
scene-related increase in coupling with the PPA was significantly stronger in
multiple clusters in occipital cortex under visual than haptic stimulation
(Figure 2B; Table S2)''}

\todo[inline]{following phrasing might be strange but necessary to delineate
from Huth (2016); they do voxel-wise semantic modeling regarding places in PPA
but imo that does not say anything about excitation/inhibition; interestingly
Huth mentions PPA during talks but it is not discussed in any paper and despite
being promised none of his group came up with a paper regarding that topic}
% Aziz (2008): place related sentences
To our knowledge only one study \citep{aziz2008modulation} investigated how
hemodynamic activity in the PPA differs between stimulus features of spoken
language.
% Aziz' stimuli
\cite{aziz2008modulation} used sentences that described generic or famous places
(e.g. ``The Taj Mahal faces a long thin reflecting pool''), faces  (``Marilyn
Monroe has a large square jaw''), or objects (``The television has a long
antenna'').
% Aziz' tasks
Participants were instructed to press a button whenever the sentence described
an inaccurate or improbable fact.
% Aziz' results
Activation in the left, but not right, PPA was significantly reduced when
participants listened to place-related sentences compared to listening to
face-related sentences. Moreover, this effect was only observed in sentences
involving famous places.
% wtf did Aziz really do?
\todo[inline]{lass uns bitte kurz im Gespräch über Aziz Paper gucken; die
relvanten Abschnitte sind in der PDF markiert. Ihre Method Section ist
``strange'' und im Grunde kommt überall nur uneinheitliche Grütze heraus; ich
blicke nicht durch, weshalb geschriebenes nicht vollständig korrekt sein wird;
so wie ich es verstanden habe, hat sie vier 2x2 ANOVAs den Unterschied zwischen
PPA und FFA angeguckt, aber diesen Unterschied im Kontrast zu object-related
Sentences (dortige Fig 3)}

\todo[inline]{``contextual associations hypothesis''
(\citep{aminoff2006parahippocampal, aminoff2013role}) does not show up in intro
anymore; events/regressors cannot touch that issue; might be interesting during
discussion of anterior/posterior PPA.}

% summary if literature review
In summary, studies suggest that the PPA does preferably but not exclusively
respond to visually presented spatial information.
% shortcomings of previous studies: simplified stimuli
Nevertheless, all reviewed studies have in common that they employed a small set
of simplified stimuli to strictly control experimental conditions.
% shortcomings of previous studies: task-based paradigm
Further, they usually relied on explicit judgment-based tasks to ensure that
participants payed attention to the stimuli.
% disadvantage 1b: lack of validity
Paradigms using block designs accompanied with a task have the disadvantage that
they do not resemble our real-life experience and thus lack external validity
\citep{westfall2016fixing} as well as ecological validity
\citep{hasson2004intersubject}.
% disadvantage 2a: averaging for group results
Additionally, the reviewed studies averaged results across 7-11 subjects to
improve the signal-to-noise-ratio (SNR).
% disadvantage 2b: no individual level
The disadvantage here is that the averaging approach does not characterize brain
functions at an individual level, a prerequisite for the application of brain
imaging methods in individual diagnostics (cf. \cite{dubois2016building,
eickhoff2020towards}).
% open questions
This raises the question how the PPA behaves under life-like conditions, and how
group results a driven by individuals subjects especially in response to
auditory stimulus\todo{this comes out of nowhere}.

% naturalistic stimuli
Paradigms using naturalistic stimuli like movies
\citep{hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
\citep{honey2012not, lerner2011topographic, silbert2014coupled} offer complex,
continuous stimulation that better resemble the experience of our dynamic
environment.
% naturalistic stimuli review: intro
Two early studies using naturalistic stimuli suggest functional specialization
of brain areas is preserved during movie watching when many perceptual and
cognitive processes are triggered simultaneously \citep{bartels2004mapping,
hasson2004intersubject}.
% Bartels (2004): Film + GLM (but surprisingly did not annotate landscapes)
\cite{bartels2004mapping} manually annotated time points that depict faces and
human bodies in a 22 minute clip of the movie \textit{Tomorrow Never Dies}
\citep{tomorrowneverdies}.
% Bartels: results
Employing a general linear model (GLM) to model hemodynamic activity, these time
points correlated with increased activity in the ``fusiform face area''
\citep{kanwisher1997ffa} and ``extrastriate body area''
\citep{downing2001bodyarea} respectively.
% Hasson (2004): Film + (reverse) ISC
Employing a reverse intersubject correlation, \cite{hasson2004intersubject} used
a 30 minute clip of the movie \textit{The Good, the Bad, and the Ugly}
\citep{goodbadugly}.
% Hasson: method
fMRI brain volumes showing the highest hemodynamic activity in the PPA [across
(five) participants] were matched to the temporally corresponding movie frames.
% Hasson: results
Results revealed that corresponding movie frames depicted indoor and outdoor
scenes including buildings and open fields.
% summary naturalistic stimuli
Nevertheless, both studies used an audio-visual stimulus and again do not
address the question how the investigated functional areas respond during
auditory stimulation.

@@

% what we did: data source
In the current study, we analyze publicly available functional data
(studyforrest.org) of the same 14 participants watching a movie
\citep{hanke2016simultaneous} and listening to an audiobook.
\citep{hanke2014audiomovie}.
% PPA + movie + audio-description
We annotated cuts \todo{MIH: only cuts relevant?} in the movie ``Forrest Gump'' \citep{ForrestGumpMovie}, and
words spoken by an additional narrator in the movie's audio-description (i.e.
the movie's audio-only variant; \citep{ForrestGumpGermanAD}) to exploratorily
investigate how the parahippocampal gyrus behaves during more life-like
conditions free from any task.
% traditional GLM
We do this by analyzing our data by constructing GLM contrasts as canonically
used to analyze data from tightly controlled paradigms.
% focus on audio-description
Encouraged by \citep{aziz2008modulation}, we focus on the audio-description as
an exclusively auditory paradigm. We further test the audio-description's localization
performance of a ``visual area'' in individual study participants by comparing
our results to results of a dedicated visual localizer experiment done with the
same participants \citep{sengupta2016extension}.
% results
Our results demonstrate that (a), (b), (c)... \todo{similar to abstract and
conclusion}

@@

\todo[inline]{Specific data outputs should be explicitly referenced via data
citation (see Data Records and Data Citations, below)}
\todo[inline]{current order of subsections might be ``non-canonical''}
\todo[inline]{parts from original studies probably too detailed}

% intro
We used data from three publicly available datasets
(\href{http://www.studyforrest.org}{studyforrest.org}) that have already been
used by other research groups for independent research questions.
% used studies
The same subjects were
% AO
a) listening to the audio-description (AO study; \citep{hanke2014audiomovie}) of
the movie ``Forrest Gump'', a dataset already used by \citep{hu2017decoding,
nguyen2016integration},\todo{this is kind of a loveless list}
% AV
b) watching the actual audio-visual movie (AV study;
\citep{hanke2016simultaneous}), a dataset already used by
\citep{ben2018hippocampal},
% VIS
c) participating in a dedicated six-category block-design visual localizer (VIS
study; \citep{sengupta2016extension}), a dataset already used by
\citep{jiahui2019predicting}.
% see corresponding papers for details
An exhaustive description of the participants, stimulus creation, procedure,
stimulation setup, and fMRI acquisition can be found in the corresponding
publications. Following is a summary of the most important aspects.

@@

\subsection{Naturalistic stimuli annotation}
% todo stimuli were not designed for research purposes
Both natural stimuli were originally designed to entertain their audiences and
to capture attention free from any perceptual or behavioral task.
% AO annotation
Thus for the analysis of the AO data, we extended an publicly available
annotation of speech \citep{haeusler2020speechanno} by further annotating words
spoken by the audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content.
% categories in detail
Nouns were categorized by the verbal clue they provide about the cinematographic
scene's environment (\texttt{geo}, \texttt{geo-room}; \texttt{setting\_new},
\texttt{setting\_old}), its inherent persons (e.g. \texttt{female},
\texttt{male}, \texttt{persons}), a person's body or worn clothes
(\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a scene's
inherent objects (\texttt{object}, \texttt{furniture}).
% why and how of categories 1
Some categories were created to reflect the six stimulus categories used in the
visual localizer experiment (e.g. \texttt{geo}, \texttt{object}).
% why and how of categories 2
Other categories were created to semantically cluster some remaining nouns into
additional categories (e.g. \texttt{fname}, \texttt{furniture})
% problem with hierarchical categories
\todo[inline]{compare the following with Methods: AO contrasts \& Discussion}
Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec}
comprise not just words that describe an abstract location (e.g. ``in
Greenbow'') or a setting as whole (e.g. ``the platoon wades through a rice
field'', ``in a disco''). They also comprise words that could count as a member
of another categories in case the narrator uses these words to indicate a switch
from one setting to another (e.g. ``near an old bus'').
% reference to table with rules and examples
A complete overview of all 19 categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with counts
The resulting counts for the whole stimulus and the eight stimulus segments used
during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.

@@

% AO
In the AO study, a whole-body \unit[7]{Tesla} Siemens MAGNETOM magnetic
resonance scanner equipped with a local circularly polarized head transmit and a
32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired
T2*-weighted echo-planar images (gradient-echo, \unit[2]{s} repetition time
(TR), \unit[22]{ms} echo time, \unit[0.78]{ms} echo spacing, \unit[1488]{Hz/Px}
bandwidth, generalized autocalibrating partially parallel acquisition,
acceleration factor 3, \unit[2]{Hz/Px} bandwidth in phase encoding direction).
% slices & FOV
36 axial slices (thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane
resolution, \unit[224]{mm} field-of-view, anterior-to-posterior phase encoding
direction) with a \unit[10]{\%} inter-slice gap were recorded in ascending
order.  Slices were oriented to include the ventral portions of frontal and
occipital cortex while minimizing intersection with the eyeballs. The field of
view was centered on the approximate location of Heschl's gyrus.
% motion correction
EPI images were online-corrected for motion and geometric distortions [Oh, S. et
al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011]\todo{references to
bib if this paragraph stays in the paper}. Auxiliary scans for slice alignment
and motion- and distortion-correction were performed at the beginning of the
first fMRI recording session and also after the break at the start of the
recording for the second half of the movie.
% AV & VIS
In the AV and VIS study, a whole-body \unit[3]{Tesla} Philips Achieva dStream
MRI scanner equipped with a 32 channel head coil acquired T2*-weighted
echo-planar images (gradient-echo, \unit[2]{s} repetition time, \unit[30]{ms}
echo time, \unit[90]{$^{\circ}$} flip angle, \unit[1943]{Hz/Px} bandwidth,
parallel acquisition with sensitivity encoding (SENSE) reduction factor 2).
% slices
35 axial slices (thickness \unit[3.0]{mm}, \unit[10]{\%} inter-slice gap) with
\unit[80 $\times$ 80]{voxels} (\unit[3.0 $\times$ 3.0]{mm} of in-plane
resolution, \unit[240]{mm} field-of-view) and an anterior-to-posterior phase
encoding direction were recorded in ascending order. Philips' ``SmartExam'' was
used to automatically position slices in AC-PC orientation such that the topmost
slice was located at the superior edge of the brain. This automatic slice
positioning procedure was identical in the AV and VIS study, and yielded a
congruent geometry across paradigms.

@@

\todo[inline]{I revised part of motion correction/co-registration but as usually
I am pretty unsure about correctness}
\todo[inline]{what is missing: As I see it, AO must have been downsampled
to 2.5x2.5x2.5 mm and AV must have been upsampled from 3.0 to 2.5mm}

@@

@@

\todo[inline]{change coordinates of figure to z=-11 as it is in the slices of
individuals}

@@

% Precuneus = retrosplenial cortex ?
\todo[inline]{Seven of eight contrasts show bilaterally significant clusters in
the retrosplenial region (and ventral precuneus)}.

@@

% but
Results also suggest that localization performance depends on the
amount of available data and how well the feature space is modeled.
% what's going on
Despite performing a whole brain analysis, we do not find many (random) clusters
in single contrasts or even systematically across contrasts that hamper the
interpretation of results.\todo[inline]{god forgive me for this paragraph}.
% null results regarding attention and eye movements
For example in the AV results, we do not find significant clusters that could be
attributed to cognitive processes like attention, eye movements, or
memory.\todo{which kind of memory}

@@

% Aminoff (2013)
Aminoff (2013) in general: processing of strong,
long-term, contextual associations elicits activity within the PHC, as well as
the RSC (which includes regions of the retrosplenial cortex, extending into the
posterior cingulate cortex, and the precuneus), the medial prefrontal cortex
(MPFC), and the transverse occipital sulcus (TOS) (Figure 2) [2,3,59–67].

@@

% natural stimulation
Intro: Natural stimuli like movies \citep{hasson2008neurocinematics,
sonkusare2019naturalistic} or narratives \citep{honey2012not,
lerner2011topographic, silbert2014coupled} offer an easy to implement,
(continuous,) complex, immersive, task-free paradigm that more closely resembles
our natural dynamic environment than traditional experimental designs.
% why naturalisti stimuli are so cool
(see also \citep{sonkusare2019naturalistic, eickhoff2020towards,
hamilton2018revolution})
% re-use of data for independent research question
Due to their continuity, complexity, and length, they offer a vast amount of
data on a variety of brain functions like low-level perception, attention,
comprehension, memory, emotions, or social interactions. This suggests the data
can later be reused for variety of totally different, independent research
questions, possibly on an individual level; increased compliance in individual
diagnostics in ``special'' populations where compliance is more difficult to
archive (pediatric or psychiatric)

>>>>

\section{Introduction}

\todo[inline]{Limit for main text (intro and discussion) = ca. 3k words;
intro is about 1k words (with to dos)}

\todo[inline]{studies regarding naturalistic stimuli are dropped (Hasson,
2004: reverse correlation in PPA; Bartels, 2004: FFA and EBA). That should be
okay since we focus on the auditory part which should be clearer now; Hasson /
Bartels might shortly be mentioned in the discussion though}

@@

% brain mapping via fMRI
Humans can perceive and make sense of their daily environment casually and
seemingly without any effort. Cognitive neuroscientists use brain imaging
techniques to map seemingly effortless perceptual and cognitive processes like
seeing and recognizing faces (e.g. \citep{kanwisher1997ffa}) to functional brain
areas or networks.
% What is the PPA?
A classic example of a higher-level visual area is the ``parahippocampal place
area'' (PPA) \citep{epstein1998ppa, epstein1999parahippocampal}.
% anatomical location != functional location
The PPA is located in the posterior parahippocampal gyrus including adjacent
regions of the fusiform gyrus and anterior lingual gyrus
\citep{epstein2008parahippocampal}, and thus not anatomically but functionally
defined:
% neural correlate of scene perception
increased hemodynamic activity is observed in the PPA when subjects view
pictures of landscapes, buildings or landmarks (compared to e.g. pictures of
tools or faces) during blood oxygenation level-dependent functional magnetic
resonance imaging (BOLD fMRI) \citep{aguirre1998area, epstein2014neural,
epstein1998ppa}.

\todo[inline]{The following review of O'Craven and Wolbers could be shortened.
Keeping the small paragraph regarding Aziz should make the focus on auditory
perception clearer. What do you think?}
% literature review overview 1: imagination & haptic exploration
Increased hemodynamic activity in the PPA generalizes to mental imagination of
landscapes \citep{ocraven2000mental} and haptic exploration of scenes
constructed from LEGO blocks \citep{wolbers2011modality}.
% O'Craven: watching pictures
In a study conducted by \cite{ocraven2000mental} participants viewed alternating
blocks of pictures showing famous faces and familiar places during an initial
experimental paradigm.
% O'Craven: mental imagery
In a subsequent paradigm, participants were instructed to ``form a vivid mental
image'' of the previously viewed pictures.
% O'Craven results
The PPA showed increased activation during imagination of places compared to
faces but the imagination tasks showed a smaller activation level compared to
the perceptual task.
% Wolbers: haptic exploration
In a block design study conducted by \cite{wolbers2011modality} the PPA of
[sighted] participants showed increased activation during a delayed
match-to-sample task of haptically explored scenes constructed from LEGO bricks
compared to haptically explored abstract geometric objects.
% Wolbers: connectivity analysis
\todo[inline]{Wolbers performed connectivity analysis between PPA and occipital
    cortex, and compares connectivity during visual and haptic paradigm: ``The
    scene-related increase in coupling with the PPA was significantly stronger
    in multiple clusters in occipital cortex under visual than haptic
stimulation (Figure 2B; Table S2)''}

\todo[inline]{following phrasing might be strange but necessary to delineate
from Huth (2016); they do voxel-wise semantic modeling regarding places in PPA
but imo that does not say anything about excitation/inhibition; interestingly
Huth mentions PPA during talks but it is not discussed in any paper and despite
being promised none of his group came up with a paper regarding that topic}

% Aziz (2008): place related sentences
To our knowledge only one study \citep{aziz2008modulation} investigated how
hemodynamic activity in the PPA differs between different semantic stimulus
categories occuring in spoken language.
% Aziz' stimuli
\cite{aziz2008modulation} used sentences that described generic or famous places
(e.g. ``The Taj Mahal faces a long thin reflecting pool''), faces (``Marilyn
Monroe has a large square jaw''), or objects (``The television has a long
antenna'').
% Aziz' tasks
Participants were instructed to press a button whenever the sentence described
an inaccurate or improbable fact.
% Aziz' results
Activation in the left, but not right, PPA was significantly reduced when
participants listened to place-related sentences compared to listening to
face-related sentences. Moreover, this effect was only observed in sentences
involving famous places.
% wtf did Aziz really do?
\todo[inline]{lass uns bitte kurz im Gespräch über Aziz Paper gucken; die
relvanten Abschnitte sind in der PDF markiert. Ihre Method Section ist
``strange'' und im Grunde kommt überall nur uneinheitliche Grütze heraus; ich
blicke nicht durch, weshalb geschriebenes nicht vollständig korrekt sein wird;
so wie ich es verstanden habe, hat sie vier 2x2 ANOVAs den Unterschied zwischen
PPA und FFA angeguckt, aber diesen Unterschied im Kontrast zu object-related
Sentences (dortige Fig 3)}

% summary if literature review
In summary, studies suggest that the PPA does preferably but not exclusively
respond to visually presented spatial information.
% three things in common
Nevertheless, the reviewed studies usually had three things in common.
% designed stimulus set
First, they employed a small sets of carefully chosen stimuli. Further, stimuli
were conceptualized to control confounding variables (e.g. color, luminance,
size, sentence length), a process that is often not reported in
detail.\todo{check that}
% block-design & task
Second, studies used block-designed paradigms to maximize detection power.
Further, they usually employed explicit perceptual judgment to keep participants
paying attention to the stimuli.
% averaging
Third, the reviewed studies averaged results across 7-11 subjects to improve
signal-to-noise ratio (SNR).
% disadvantages
Conceptualized stimuli, block-design experiments and the averaging approach have
their merits but also disandvantages.
% designed stimulus set
First, small sets of conceptualized stimuli presented on experimental blocks
poorly resembles our rich and multidimensional environment that our brains are
accommodated to [sonkusare2019naturalistic].
% block-design & task
Second, study participants can and will become aware about which perceptual
process is examined in the study by merely being exposed to the experimental
paradigm.
% inference: validity is poor
Thus, small sets of conceptualized stimuli and block-design experiment lack
external validity \citep{westfall2016fixing} as well as ecological validity
\citep{hasson2004intersubject}.
% disadvantage of averaging
Lastly, averaging data across subjects increases the SNR but does not
characterize brain functions at an individual level, a prerequisite for the
application of brain imaging methods in individual diagnostics (cf.
\cite{dubois2016building, eickhoff2020towards}).

% We are different
In this study, we operationalize the perception of landscapes and landmarks
(compared to e.g. faces and objects) differently from the reviewed studies by
using two fixed naturalistic stimuli (see \citep{hamilton2018revolution,
hasson2008neurocinematics, sonkusare2019naturalistic} for reviews).
% open research question
Here, we investigate if increased activation in the PPA correlates with
incidental ``spatial events'' in a Hollywood movie and its corresponding
audio-description (i.e. the audio-only variant of the movie).
% annotation
We annotated words spoken by the narrator of the audio-description of the movie
``Forrest Gump'' \citep{ForrestGumpMovie} as well as cuts and depicted locations
in the audio-visual movie to be able to operationalize the perception of
landscapes and landmarks (compared to e.g. persons and objects).
% public data
We then analyze publicly available data
(\href{http://www.studyforrest.org}{studyforrest.org}) from the same subjects
that listened to the audio-description and watched the movie during fMRI
scanning.
% first: group level AO
First, general linear model (GLM) contrasts based on the audio-description's
annotation are used to test if we could isolate the PPA with an auditory
stimulus on a group level.
% second: group level AV
Second as conceptual/cross-modal control, we compare results of the
audio-description to results based on the annotation of the movie.
% individual results
Lastly focussing on the audio-description, we compare results on the level of
individual subjects to results of a block-designed visual localizer experiment
done with the same individuals \citep{sengupta2016extension}.
% results
\todo[inline]{following paragraph will be similar to abstract and conclusion}
Our results demonstrate that (a), (b), (c).

@@

\todo[inline]{current order of subsections might be ``non-canonical''}

\todo[inline]{parts from original studies probably too detailed}

\todo[inline]{Specific data outputs should be explicitly referenced via data
citation (see Data Records and Data Citations, below)}

% intro
We used data from three publicly available datasets
(\href{http://www.studyforrest.org}{studyforrest.org}) that have already been
used by other research groups for independent research questions.
% used studies
The same subjects were
% AO
a) listening to the audio-description (AO study; \citep{hanke2014audiomovie}) of
the movie ``Forrest Gump'', a dataset already used by \citep{hu2017decoding,
nguyen2016integration},
% AV
b) watching the actual audio-visual movie (AV study;
\citep{hanke2016simultaneous}), a dataset already used by
\citep{ben2018hippocampal},
% VIS
c) participating in a dedicated six-category block-design visual localizer (VIS
study; \citep{sengupta2016extension}), a dataset already used by
\citep{jiahui2019predicting}.
% see corresponding papers for details
An exhaustive description of the participants, stimulus creation, procedure,
stimulation setup, and fMRI acquisition can be found in the corresponding
publications. Following is a summary of the most important aspects.

@@

\subsection{Naturalistic stimuli annotation}
% todo stimuli were not designed for research purposes
Both natural stimuli were not design to isolate a specific brain area but to
entertain their audiences free from any perceptual or behavioral task.
% fixed stimuli and operationalization
We annotated the temporal structure of the fixed stimuls material to
operationalize the perception of different stimulus features (e.g. the
perception of landmarks and faces) and create GLM contrasts in the subsequent
data analysis.
% AO annotation
For the analysis of the AO data, we extended an publicly available annotation of
speech \citep{haeusler2020speechanno} by further annotating words spoken by the
audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content.
% categories in detail
Nouns were categorized by the verbal clue they provide about the cinematographic
scene's environment (\texttt{geo}, \texttt{geo-room}; \texttt{setting\_new},
\texttt{setting\_old}), its inherent persons (e.g. \texttt{female},
\texttt{male}, \texttt{persons}), a person's body or worn clothes
(\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a scene's
inherent objects (\texttt{object}, \texttt{furniture}).
% why and how of categories 1
Some categories were created to reflect the six stimulus categories used in the
visual localizer experiment (e.g. \texttt{geo}, \texttt{object}).
% why and how of categories 2
Other categories were created to semantically cluster some remaining nouns into
additional categories (e.g. \texttt{fname}, \texttt{furniture})
% problem with hierarchical categories
Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
not just words that describe an abstract location (e.g. ``in Greenbow'') or a
setting as whole (e.g. ``the platoon wades through a rice field'', ``in a
disco''). They also comprise words that could count as a member of another
categories in case the narrator uses these words to indicate a switch from one
setting to another (e.g. ``near an old bus'').
% reference to table with rules and examples
A complete overview of all 19 categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with counts
The resulting counts for the whole stimulus and the eight stimulus segments used
during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.

@@

% AO
In the AO study, a whole-body \unit[7]{Tesla} Siemens MAGNETOM magnetic
resonance scanner equipped with a local circularly polarized head transmit and a
32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired
T2*-weighted echo-planar images (gradient-echo, \unit[2]{s} repetition time
(TR), \unit[22]{ms} echo time, \unit[0.78]{ms} echo spacing, \unit[1488]{Hz/Px}
bandwidth, generalized autocalibrating partially parallel acquisition,
acceleration factor 3, \unit[2]{Hz/Px} bandwidth in phase encoding direction).
% slices
36 axial slices (thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane
resolution, \unit[224]{mm} field-of-view, anterior-to-posterior phase encoding
direction) with a \unit[10]{\%} inter-slice gap were recorded in ascending
order.
% slice orientation
Slices were oriented to include the ventral portions of frontal and occipital
cortex while minimizing intersection with the eyeballs.
% FOV
The field of view was centered on the approximate location of Heschl's gyrus.
% motion correction
EPI images were online-corrected for motion and geometric distortions [+++Oh, S.
et al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011+++]
% auxiliary scans
Auxiliary scans for slice alignment and motion- and distortion-correction were
performed at the beginning of the first fMRI recording session and also after
the break at the start of the recording for the second half of the movie.
% AV & VIS
In the AV and VIS study, a whole-body \unit[3]{Tesla} Philips Achieva dStream
MRI scanner equipped with a 32 channel head coil acquired T2*-weighted
echo-planar images (gradient-echo, \unit[2]{s} repetition time, \unit[30]{ms}
echo time, \unit[90]{$^{\circ}$} flip angle, \unit[1943]{Hz/Px} bandwidth,
parallel acquisition with sensitivity encoding (SENSE) reduction factor 2).
% slices
35 axial slices (thickness \unit[3.0]{mm}, \unit[10]{\%} inter-slice gap) with
\unit[80 $\times$ 80]{voxels} (\unit[3.0 $\times$ 3.0]{mm} of in-plane
resolution, \unit[240]{mm} field-of-view) and an anterior-to-posterior phase
encoding direction were recorded in ascending order.
% slice positioning
Philips' ``SmartExam'' was used to automatically position slices in AC-PC
orientation such that the topmost slice was located at the superior edge of the
brain. This automatic slice positioning procedure was identical in the AV and
VIS study, and yielded a congruent geometry across paradigms.

@@

\todo[inline]{part regarding motion correction/co-registration might be
incorrect}

\todo[inline]{what is missing: As I see it, AO must have been downsampled
to 2.5x2.5x2.5 mm and AV must have been upsampled from 3.0 to 2.5mm??}

@@

 \todo[inline]{I wonder whether we should make a general
    point: The construction of contrasts of interests feels "messy". But this is
    a consequence of the inability to filter the stimulus material. That "messy"
    part is usually not obvious from a manuscript.  Here we have a fixed,
complex stimulus, and we have to operationalize our questions with whatever we
have at hand. This is not necessarily exact, and looking at the robustness is a
feature, not a problem}

@@

@@

% Precuneus = retrosplenial cortex ?
\todo[inline]{Seven of eight contrasts show bilaterally significant clusters in
the retrosplenial region (and ventral precuneus)}

@@

% but
Results also suggest that localization performance depends on the
amount of available data and how well the feature space is modeled.
% what's going on
Despite performing a whole brain analysis, we do not find many (random) clusters
in single contrasts or even systematically across contrasts that hamper the
interpretation of results.\todo[inline]{god forgive me for this paragraph}
% null results regarding attention and eye movements
For example in the AV results, we do not find significant clusters that could be
attributed to cognitive processes like attention, eye movements, or
memory.\todo{which kind of memory}

@@

% Aminoff (2013)
\citep{aminoff2006parahippocampal, aminoff2013role}; Aminoff (2013) in general:
processing of strong, long-term, contextual associations elicits activity within
the PHC, as well as the RSC (which includes regions of the retrosplenial cortex,
extending into the posterior cingulate cortex, and the precuneus), the medial
prefrontal cortex (MPFC), and the transverse occipital sulcus (TOS) (Figure 2)
[2,3,59–67].

@@

% natural stimulation
Intro: Natural stimuli like movies \citep{hasson2008neurocinematics,
sonkusare2019naturalistic} or narratives \citep{honey2012not,
lerner2011topographic, silbert2014coupled} offer an easy to implement,
(continuous,) complex, immersive, task-free paradigm that more closely resembles
our natural dynamic environment than traditional experimental designs.
% why naturalisti stimuli are so cool
(see also \citep{sonkusare2019naturalistic, eickhoff2020towards,hamilton2018revolution})
% re-use of data for independent research question
Due to their continuity, complexity, and length, they offer a vast amount of
data on a variety of brain functions like low-level perception, attention,
comprehension, memory, emotions, or social interactions. This suggests the data
can later be reused for variety of totally different, independent research
questions, possibly on an individual level; increased compliance in individual
diagnostics in ``special'' populations where compliance is more difficult to
archive (pediatric or psychiatric)
